---
title: "Northeast Atlantic Mackerel MSE"
subtitle: "**MSE for Reference Case**"
author: "L Kell & J Bentley"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
mathjax: TRUE
tags: FLR FLCore introduction
license: Creative Commons Attribution-ShareAlike 4.0 International Public License
#bibliography: ../refs.bib
#knit: (function(inputFile, encoding) {
#  rmarkdown::render(inputFile, encoding = encoding, output_dir = "../outputs/html") })
---

```{r, eval=!FALSE}
setwd("C:/flrpapers/erp_nea_mackerel/Rmd")
```
  
# Introduction

The Operating Model is based on the ICES stock assessment. All coding is done using R [@R] and FLR [@kell2007flr] in Rmarkdown [@Rmdbook], and summarised in as vignettes. The information (data, files, etc.) required to re-do the analysis, is  available at **???**, including the ICES assessment data set, and the inputs and outputs from the ecosystem models. 

Code for cleaning the input data, and R libraries used for the analysis, are contained in the 'Rmd' files such as this one. Only Key steps in the analysis are shown in the documents generated, code used for plotting are not echoed in the output but can be found in the 'Rmd' file. 

This vignette is divided into sections for [Installation](#install) of the required libraries, sourcing bespoke functions, and loading the data, before the [Operating Condition](#cond) is conducted. Hypotheses about [Natural Mortality](#m) and [Stock Rcruitment](#sr) are then  fitted.
 

Details on [Funding](#funds), [Software Versions](#pkgs) and[References](#bib) can be found at the end of the document.

```{r, knitr, eval=TRUE, warning=FALSE, cache=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# getwd()
library(knitr)
opts_chunk$set(comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE, 
               eval      =TRUE,
               cache     =TRUE,
               cache.path="cache/3_MSE/",
               fig.path  ="../outputs/figs/3_MSE",
               fig.width =8,
               fig.height=6,
               dev       ="png")
iFig=0
iTab=0
```

[](#top)


```{r, pkgs, echo=TRUE, eval=TRUE}
library(FLCore) 
library(ggplotFL)
library(ggpubr)
library(FLBRP)
library(FLasher)
library(FLAssess)

library(plyr)
library(dplyr)
library(reshape)

library(FLife)
library(FLBRP)
library(FLCandy)

library(FLSRTMB)
library(patchwork)

library(stockassessment)
library(FLfse)

library(FishLife)

theme_set(theme_bw(16))
```

```{r}
source("../R/hcrICESV3.R")
source("../R/mFn.R")
source("../R/eqFn.R") 
```

```{r, load}
load("../data/inputs/ices/ices.RData")
load("../data/inputs/ices/icesRefs.RData")

load("../data/om/err.RData")
load("../data/om/condOms.RData")
load("../data/om/recDevs.RData")
```

```{r, hcr, fig.width=8, fig.height=4, echo=FALSE}
ggplot(data.frame(x=c(0,0.5,2),y=c(0,1,1)))+
  geom_line(aes(x,y))+
  geom_vline(aes(xintercept=0.5),col="red", linetype=2)+
  geom_hline(aes(yintercept=1),  col="blue",linetype=2)+
  xlab("SSB")+ylab("Fishing Mortality")+
  scale_x_continuous(breaks=0.5,labels=expression(MSY[Btrigger]))+
  scale_y_continuous(breaks=1.0,labels=expression(F[MSY]),limits=c(0,1.2))+
  theme_bw()
```

**Figure `r iFig=iFig+1;iFig`** Harvest Control Rule

### Data

The data are the ICES inputs and historical estimates [@ICES2023] generated by "10_ICES" which runs the ICES assessment

```{r, data, echo=TRUE}
par=as(model.frame(mcf(FLQuants(ftar=refs[["fmsy"]],
                                btrig=refs[["msybtrigger"]],
                                fmin=refs[["fmsy"]]%=%0.005,
                                bmin=refs[["blim"]]%=%0,
                                blim=refs[["blim"]])),drop=T)[,-1],"FLPar")
par["ftar"][ is.na(par["ftar"])] =min(par["ftar"], na.rm=T)
par["btrig"][is.na(par["btrig"])]=min(par["btrig"],na.rm=T)
par["blim"][ is.na(par["blim"])] =min(par["blim"], na.rm=T)

ref2021=FLPar(laply(refs,window, end=2021, start=2021))
dimnames(ref2021)$params=c("Flim","Fpa","Fmsy","Fcap","Blim","Bpa","MSYBtrigger")
```

## Assessment Bias

```{r, bias, echo=TRUE}
plot(oms[c(2,1,3,5)])

bias=ldply(oms[c("M=0.15","North Sea","Barents Sea")], function(x) 
                   model.frame(FLQuants(F  =fbar(oms[["Reference"]])%/%fbar(x),
                                        SSB=ssb( oms[["Reference"]])%/%ssb( x)),drop=TRUE))
ggplot(bias)+
  geom_point(aes(F,SSB,col=.id))

biasMatrix=ddply(bias,.(.id), with, data.frame(F=mean(F),SSB=median(SSB)))
biasMatrix[2,1]="Reference"
```

## Reference Case and Robustness Set

**SRR**

+ Steepness prior
+ Steepness = 0.9
+ Depensation


**Natural Mortality**

+ Trend
+ High

## MSE

### Robustness set

```{r, eval=FALSE}
library(foreach)
library(doParallel)

nits    =500
start   =2001
end     =2020
interval=1
lag     =1

scen=data.frame(OM      =rep(c(rep("Reference",3),"Barents Sea","North Sea"),2),
                SRR     =rep(c("Prior","h=0.9","Depensation","Prior","Prior"),      2),
                Recruits=rep(c("Regime","AR"),each=5))

set.seed(1233)

shortCut=rlnorm( nits,FLQuant(0,dimnames=list(year=start:end)),var(err[-1,1])^0.5)

ncore=detectCores() - 4  
registerDoParallel(ncore)

robustness=foreach(i=seq(dim(scen)[1]), 
                     .combine   =list, 
                     .maxcombine=dim(scen)[1], 
                     .packages  =c("FLCore","FLBRP","FLasher","FLCandy")
                     ) %dopar% {
      
      source("../R/hcrICESV3.R")
                       
      with(scen[i,],hcrICES(propagate(oms[[OM]],nits),eqs[[OM]][[SRR]],
                recDevs[[Recruits]],par,start,end,interval,lag=lag,err=shortCut*subset(biasMatrix,.id==OM)$SSB,
                         bndTac=c(0.8,1.25)))[[1]]}

stopImplicitCluster()


#robustness=mlply(scen, function(OM,SRR,Recruits){
#      print(paste(OM,SRR,Recruits))
#        hcrICES(propagate(oms[[OM]],nits),eqs[[OM]][[SRR]],
#                recDevs[[Recruits]],par,start,end,interval,lag=lag,err=shortCut*subset(biasMatrix,.id==OM)$SSB,
#                         bndTac=c(0.8,1.25))[[1]]})

save(robustness,scen,file="../data/results/robustness.RData")
```

```{r}
load("../data/results/robustness.RData")

x=FLStocks(robustness)
x["ICES"]=ices
plot(x)
```

**Figure `r iFig=iFig+1;iFig`** 


```{r, results, eval=TRUE}
load("../data/results/robustness.RData")
load("../data/om/condOms.RData")

msy=ddply(crvs,.(OM,SRR), with, data.frame(
                                    Biomass =Biomass[ Catch==max(Catch)],
                                    SSB     =SSB[     Catch==max(Catch)],
                                    Recruits=Recruits[Catch==max(Catch)],
                                    Catch   =Catch[   Catch==max(Catch)],
                                    F       =F[       Catch==max(Catch)],
                                    Forage  =Forage[  Catch==max(Catch)]))
names(msy)[2]="SRR"

vrg =ldply(eqs, ldply, function(x) t(vrgFn(x)))
names(vrg)[1]="SRR"
vrg =cbind(OM=rep(names(eqs),each=3),vrg,Catch=0,F=0)

rfs=merge(msy,vrg, by=c("OM","SRR"))
names(rfs)=gsub("\\.x",".msy",   names(rfs))
names(rfs)=gsub("\\.y",".virgin",names(rfs))

blim=ddply(crvs, .(OM,SRR), subset, seq(length(Recruits))==which.min(abs(0.3 - Recruits/max(Recruits))))
rfs =merge(rfs,blim,by=c("OM","SRR"))
names(rfs)[15:20]=paste(names(rfs)[15:20],"blim",sep=".")


rf2=transmute(rfs,OM=OM,SRR=SRR,
              SSB     =SSB.msy/SSB.virgin,
              Recruits=Recruits.msy/Recruits.virgin)

F       =FLQuants(mlply(seq(10), function(i) fbar( robustness[[i]])/
                      subset(rfs,OM==scen[i,"OM"]&SRR==scen[i,"SRR"])$F.msy))
SSB     =FLQuants(mlply(seq(10), function(i) ssb(  robustness[[i]])/
                      subset(rfs,OM==scen[i,"OM"]&SRR==scen[i,"SRR"])$SSB.msy))
Catch   =FLQuants(mlply(seq(10), function(i) catch(robustness[[i]])/
                      subset(rfs,OM==scen[i,"OM"]&SRR==scen[i,"SRR"])$Catch.msy))
Recruits=FLQuants(mlply(seq(10), function(i) rec(  robustness[[i]])/
                      subset(rfs,OM==scen[i,"OM"]&SRR==scen[i,"SRR"])$Recruits.msy))
Forage  =FLQuants(mlply(seq(10), function(i) forage(robustness[[i]])/
                      subset(rfs,OM==scen[i,"OM"]&SRR==scen[i,"SRR"])$Forage.msy))

rfLn=data.frame(Regime=c("Average","High","Low"),
           level =c(1,exp(mean(subset(rsdl,year<=2010)$hat)),
                      exp(mean(subset(rsdl,year> 2010)$hat))))
nms=gsub(" ","",paste(scen$OM,scen$SRR,sep="")) 
```

```{r}
library(purrr)
load("../data/om/condOms.RData")

ts=map(oms, function(x) model.frame(FLQuants(x,
                         SSB  =function(x) ssb(x),
                         F    =function(x) fbar(x),
                         Catch=function(x) catch(x)),drop=TRUE))
ts=ldply(ts)
names(ts)[1]="OM"
ts=transmute(merge(ts,msy,by="OM"),OM=OM,SRR=SRR,year=year,
                                   F    =F.x/F.y,
                                   Catch=Catch.x/Catch.y,
                                   SSB  =SSB.x/SSB.y)

ggplot(melt(ts,c("OM","SRR","year")))+
  geom_line( aes(year,value,col=SRR))+
  geom_hline(aes(yintercept=1))+
  facet_grid(OM~variable)
save(ts,file="../data/results/ts.RData")
```

```{r}
source("../R/ABI.R") 

for (i in seq(dim(scen)[1])){
  refpts(eqs[[scen[i,"OM"]]][[scen[i,"SRR"]]])["msy",
            c("ssb","rec","yield","harvest")]=
    unlist(c(subset(rfs,OM==scen[i,"OM"]&SRR==scen[i,"SRR"])[,c("SSB.msy","Recruits.msy","Catch.msy","F.msy")]))}

abi=mlply(seq(10), function(.id) 
  ABI(robustness[[.id]],eqs[[scen[.id,"OM"]]][[scen[.id,"SRR"]]]))
```

```{r, brebuild}
load("../data/results/robustness.RData") 
ssb=mdply(seq(length(robustness)), function(x) as.data.frame(ssb(robustness[[x]]),drop=TRUE))
ssb=cbind(scen[ssb$X1,],ssb)

for (i in seq(dim(scen)[1])){
  refpts(eqs[[scen[i,"OM"]]][[scen[i,"SRR"]]])["msy",
            c("ssb","rec","yield","harvest")]=
    unlist(c(subset(msy,OM==scen[i,"OM"]&SRR==scen[i,"SRR"])[,3:6]))}

rbt=mlply(scen[1:5,1:2], function(OM,SRR) {
      eq   =eqs[[OM]][[SRR]]
      rb   =FLCandy:::tryIt(FLCandy:::rebuild(eq))
      r2   =FLCandy:::tryIt(FLCandy:::rebuildTime(rb))
      return(cbind(r2,gt=c(gt(eq))))})
rbt=ldply(rbt)
gt =ddply(rbt,.(OM,SRR), with, data.frame(gt=gt[1]))


rebuildInterp<-function(x,y,new){
  f=splinefun(x, y)
  f(new)} 

rebuild=dlply(ssb, .(OM,SRR,Recruits), with,{
           x=rbt[rbt$OM==OM[1]&rbt$SRR==SRR[1],]
           data=data/refpts(eqs[[OM[1]]][[SRR[1]]])["msy","ssb"]
           as.FLQuant(data.frame(age="all",year=year,iter=iter,
                data=rebuildInterp(x$initial,x$year,data)))})[c(10,8,6,2,4,9,7,5,1,3)]

#abi=mlply(seq(10), function(.id) 
#  ABI(robustness[[.id]],eqs[[scen[.id,"OM"]]][[scen[.id,"SRR"]]]))
```

```{r}
results=list("F"=F,"Forage"=Forage,"SSB"=SSB,"Recruits"=Recruits,"Catch"=Catch,"ABI"=abi,"Rebuild"=rebuild)
save(results,nms,scen,msy,vrg,rfLn,gt,file="../data/results/results.RData")
```


[Back to Top](#top)

# Software Version {#pkgs}

* `r version$version.string`


* FLCore:   `r packageVersion('FLCore')`
* ggplotFL: `r packageVersion('ggplotFL')`


* FLBRP:    `r packageVersion('FLBRP')`
* FLasher:  `r packageVersion('FLasher')`
* FLAssess: `r packageVersion('FLAssess')`

* FLife:    `r packageVersion('FLife')`
* mydas:    `r packageVersion('mydas')`
* FLCandy:  `r packageVersion('FLCandy')`

* FLSRTMB:         `r packageVersion('FLSRTMB')`

* plyr:     `r packageVersion('plyr')`
* dplyr:    `r packageVersion('dplyr')`
* reshape:  `r packageVersion('reshape')`

* FLfse:    `r packageVersion('FLfse')`

* stockassessment:  `r packageVersion('stockassessment')`
* FishLife:         `r packageVersion('FLAssess')`

* patchwork:       `r packageVersion('patchwork')`

* **Compiled**: `r date()`
* **Git Hash**: `r system("git log --pretty=format:'%h' -n 1", intern=TRUE)`

[Back to Top](#top)

# Funding {#funds}

[Back to Top](#top)


# References {#bib}

[Back to Top](#top)
