---
title: "Northeast Atlantic Mackerel MSE"
subtitle: "**Results**"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
mathjax: TRUE
fig_width: 6 
fig_height: 4 
tags: FLR FLCore introduction
license: Creative Commons Attribution-ShareAlike 4.0 International Public License
#bibliography: ../refs.bib
editor_options: 
  markdown: 
    wrap: 72
#knit: (function(inputFile, encoding) {
#  rmarkdown::render(inputFile, encoding=encoding, output_dir="../outputs/html") })
---

```{r, setwd, eval=FALSE}
setwd("C:/flrpapers/erp_nea_mackerel/Rmd")
```

```{r, knitr, echo=FALSE, warning=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo=FALSE)
# getwd()
library(knitr)
opts_chunk$set(comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE, 
               eval      =TRUE,
               cache     =TRUE,
               cache.path= "cache/4_Paper/",
               fig.path  ="../output/figs/4_Paper-",
               fig.width =8,
               fig.height=8,
               dev       ="png")
iFig=0
iTab=0
```

```{r, libs}
library(ggplot2); theme_set(theme_bw())  

library(FLCore)
library(FLBRP)
library(FLasher)
library(ggplotFL)
library(ggridges)
library(ggExtra)
library(ggside)
library(ggnewscale)
library(ggh4x)
library(FLife)
library(mydas)

library(ggpubr)

library(plyr)
library(dplyr)
library(tidyr)
library(reshape)

library(patchwork)
library(purrr)

library(scales)
```


```{r, source}
source("../R/abi.R")
source("../R/eqFn.R")
source("../R/boxFn.R")
source("../R/rebuild.R")
source("../R/mFn.R")
```


```{r,srr1, fig.width=7,fig.height=6}
load("../data/om/condOms.RData")  

plot(srs[["Reference"]])+xlab("SSB")+ylab("Recruits")+
  theme_bw(16)+
  theme(legend.position="bottom")
```

**Figure `r iFig=iFig+1; iFig`** Stock recruitment relationship fits

  
```{r, cond-robustness-eq, fig.width=7,fig.height=6}
ggplot(crvs)+
  geom_line(aes(SSB/1000,Catch/1000,col=SRR))+
  facet_wrap(~OM)+ 
  scale_color_manual("SRR",values=rainbow(3))+
  theme(legend.position="bottom")
```

**Figure `r iFig=iFig+1; iFig`** Production functions


```{r, ts}
load("../data/results/robustness.RData")
load("../data/om/cvrs.RData")
load("../data/results/results.RData")

for (i in seq(dim(scen)[1])){ 
  refpts(eqs[[scen[i,"OM"]]][[scen[i,"SRR"]]])["msy",
            c("ssb","rec","yield","harvest")]=
    unlist(c(subset(msy,OM==scen[i,"OM"]&SRR==scen[i,"SRR"])[,3:6]))
}

# msy=ddply(crvs,.(OM,.id), with, data.frame(
#                                     SSB     =SSB[     Catch==max(Catch)],
#                                     Recruits=Recruits[Catch==max(Catch)],
#                                     Catch   =Catch[   Catch==max(Catch)],
#                                     F       =F[       Catch==max(Catch)]))
# names(msy)[2]="SRR"
# scen=data.frame(OM =c(rep("Reference",3),"Environmental\nDriver","High M"),
#                 SRR=c("Prior","h=0.9","Depensation","Prior","Prior"))
# 

vrgLn=transmute(merge(msy,vrg,by=c("OM","SRR")),
               OM=OM,SRR=SRR,
               SSB     =SSB.y/SSB.x*0.3,
               Recruits=Recruits.y/Recruits.x*0.3,
               Forage  =Forage.y/Forage.x*0.3)
vrgLn=merge(scen[1:5,-3],vrgLn)

plot(FLStocks(robustness))
```

**Figure `r iFig=iFig+1;iFig`** 

```{r, p}
nms2=c("Reference","SRR:0.9","SRR:Depen","M:Driver","M:High") 

F=results$F
ggarrange(plot(F[1:5 ],probs=c(0.05,0.33,0.5,0.66,0.95),iter=123)+
            facet_grid(factor(qname,levels=1:5,labels=nms2)~., labeller=label_parsed)+
            geom_hline(aes(yintercept=1),col="darkgreen")+
            scale_x_continuous(limits=c(1995,2020),breaks=seq(2000,2020,10))+
            scale_y_continuous(limits=c(0,3.5),breaks=c(0,1,2,3))+
            scale_colour_manual(values=c("grey50"))+
            geom_vline(aes(xintercept=2005),linetype=2)+
            geom_vline(aes(xintercept=2010),linetype=2)+
            geom_vline(aes(xintercept=2015),linetype=2)+
            xlab("Year")+ylab("F"),
          plot(F[6:10],probs=c(0.05,0.33,0.5,0.66,0.95),iter=123)+
            facet_grid(factor(qname,levels=1:5+5,labels=nms2)~., labeller=label_parsed)+
            geom_hline(aes(yintercept=1),col="darkgreen")+
            scale_x_continuous(limits=c(1995,2020),breaks=seq(2000,2020,10))+
            scale_y_continuous(limits=c(0,3.5),breaks=c(0,1,2,3))+
            scale_colour_manual(values=c("grey50"))+xlab("Year")+
            geom_vline(aes(xintercept=2005),linetype=2)+
            geom_vline(aes(xintercept=2010),linetype=2)+
            geom_vline(aes(xintercept=2015),linetype=2)+
            theme(axis.title.y=element_blank(), axis.text.y=element_blank()),
            widths=c(1,0.8))
```

**Figure `r iFig=iFig+1;iFig`** 

```{r}
SSB=results$SSB 
ggarrange(plot(SSB[1:5 ],probs=c(0.05,0.33,0.5,0.66,0.95),iter=123)+
            facet_grid(factor(qname,levels=1:5,labels=nms2)~., labeller=label_parsed)+
            geom_hline(aes(yintercept=level,linetype=Regime),
                                     data=rfLn,col="darkgreen")+
            geom_hline(aes(yintercept=SSB),col="darkred",data=cbind(qname=seq(5),vrgLn))+
            scale_x_continuous(limits=c(1995,2020),breaks=seq(2000,2020,10))+
            scale_y_continuous(limits=c(0,4),breaks=c(0,1,2,3))+
            scale_colour_manual(values=c("grey50"))+
            geom_vline(aes(xintercept=2005),linetype=2)+
            geom_vline(aes(xintercept=2010),linetype=2)+
            geom_vline(aes(xintercept=2015),linetype=2)+
            xlab("Year")+ylab("SSB"),
          plot(SSB[6:10],probs=c(0.05,0.33,0.5,0.66,0.95),iter=123)+
            facet_grid(factor(qname,levels=1:5+5,labels=nms2)~., labeller=label_parsed)+
            geom_hline(aes(yintercept=level,linetype=Regime),
                                     data=rfLn,col="darkgreen")+
            geom_hline(aes(yintercept=SSB),col="darkred",data=cbind(qname=6:10,vrgLn))+
            scale_x_continuous(limits=c(1995,2020),breaks=seq(2000,2020,10))+
            scale_y_continuous(limits=c(0,4),breaks=c(0,1,2,3))+
            scale_colour_manual(values=c("grey50"))+xlab("Year")+
            geom_vline(aes(xintercept=2005),linetype=2)+
            geom_vline(aes(xintercept=2010),linetype=2)+
            geom_vline(aes(xintercept=2015),linetype=2)+
            theme(axis.title.y=element_blank(), axis.text.y=element_blank()),
            widths=c(1,0.8))
```

**Figure `r iFig=iFig+1;iFig`** 

```{r}
Catch=results$Catch 
ggarrange(plot(Catch[1:5 ],probs=c(0.05,0.33,0.5,0.66,0.95),iter=123)+
            facet_grid(factor(qname,levels=1:5,labels=nms2)~., labeller=label_parsed)+
            geom_hline(aes(yintercept=level,linetype=Regime),
                                     data=rfLn,col="darkgreen")+
            scale_x_continuous(limits=c(1995,2020),breaks=seq(2000,2020,10))+
            scale_y_continuous(limits=c(0,3.5),breaks=c(0,1,2,3))+
            scale_colour_manual(values=c("grey50"))+
            geom_vline(aes(xintercept=2005))+
            geom_vline(aes(xintercept=2010))+
            xlab("Year")+ylab("Catch"),
          plot(Catch[6:10],probs=c(0.05,0.33,0.5,0.66,0.95),iter=123)+
            facet_grid(factor(qname,levels=1:5+5,labels=nms2)~., labeller=label_parsed)+
            geom_hline(aes(yintercept=level,linetype=Regime),
                                     data=rfLn,col="darkgreen")+
            scale_x_continuous(limits=c(1995,2020),breaks=seq(2000,2020,10))+
            scale_y_continuous(limits=c(0,3.5),breaks=c(0,1,2,3))+
            scale_colour_manual(values=c("grey50"))+xlab("Year")+
            geom_vline(aes(xintercept=2005),linetype=2)+
            geom_vline(aes(xintercept=2010),linetype=2)+
            geom_vline(aes(xintercept=2015),linetype=2)+
            theme(axis.title.y=element_blank(), axis.text.y=element_blank()),
            widths=c(1,0.8))
```

**Figure `r iFig=iFig+1;iFig`** 

```{r}
Recruits=results$Recruits 
ggarrange(plot(Recruits[1:5 ],probs=c(0.05,0.33,0.5,0.66,0.95),iter=123)+
            facet_grid(factor(qname,levels=1:5,labels=nms2)~., labeller=label_parsed)+
            geom_hline(aes(yintercept=level,linetype=Regime),
                                     data=rfLn,col="darkgreen")+
            geom_hline(aes(yintercept=Recruits),col="darkred",data=cbind(qname=seq(5),vrgLn))+
            scale_x_continuous(limits=c(1995,2020),breaks=seq(2000,2020,10))+
            scale_y_continuous(limits=c(0,3.5),breaks=c(0,1,2,3))+
            scale_colour_manual(values=c("grey50"))+
            geom_vline(aes(xintercept=2005),linetype=2)+
            geom_vline(aes(xintercept=2010),linetype=2)+
            geom_vline(aes(xintercept=2015),linetype=2)+
            xlab("Year")+ylab("Recruits"),
          plot(Recruits[6:10],probs=c(0.05,0.33,0.5,0.66,0.95),iter=123)+
            facet_grid(factor(qname,levels=1:5+5,labels=nms2)~., labeller=label_parsed)+
            geom_hline(aes(yintercept=level,linetype=Regime),
                                     data=rfLn,col="darkgreen")+
            geom_hline(aes(yintercept=Recruits),col="darkred",data=cbind(qname=6:10,vrgLn))+
            scale_x_continuous(limits=c(1995,2020),breaks=seq(2000,2020,10))+
            scale_y_continuous(limits=c(0,3.5),breaks=c(0,1,2,3))+
            scale_colour_manual(values=c("grey50"))+xlab("Year")+
            geom_vline(aes(xintercept=2005),linetype=2)+
            geom_vline(aes(xintercept=2010),linetype=2)+
            geom_vline(aes(xintercept=2015),linetype=2)+
            theme(axis.title.y=element_blank(), axis.text.y=element_blank()),
            widths=c(1,0.8))
```

**Figure `r iFig=iFig+1;iFig`** 

```{r}
Forage=results$Forage 
ggarrange(plot(Forage[1:5 ],probs=c(0.05,0.33,0.5,0.66,0.95),iter=c(123))+
            facet_grid(factor(qname,levels=1:5,labels=nms2)~., labeller=label_parsed)+
            geom_hline(aes(yintercept=level,linetype=Regime),
                                     data=rfLn,col="darkgreen")+
            geom_hline(aes(yintercept=Forage),col="darkred",data=cbind(qname=seq(5),vrgLn))+
            scale_x_continuous(limits=c(1995,2020),breaks=seq(2000,2020,10))+
            scale_y_continuous(limits=c(0,3.5),breaks=c(0,1,2,3))+
            scale_colour_manual(values=c("grey50"))+
            geom_vline(aes(xintercept=2005),linetype=2)+
            geom_vline(aes(xintercept=2010),linetype=2)+
            geom_vline(aes(xintercept=2015),linetype=2)+
            xlab("Year")+ylab("Forage"),
          plot(Forage[6:10],probs=c(0.05,0.33,0.5,0.66,0.95),iter=c(123))+
            facet_grid(factor(qname,levels=1:5+5,labels=nms2)~., labeller=label_parsed)+
            geom_hline(aes(yintercept=level,linetype=Regime),
                                     data=rfLn,col="darkgreen")+
            geom_hline(aes(yintercept=Forage),col="darkred",data=cbind(qname=6:10,vrgLn))+
            scale_x_continuous(limits=c(1995,2020),breaks=seq(2000,2020,10))+
            scale_y_continuous(limits=c(0,3.5),breaks=c(0,1,2,3))+
            scale_colour_manual(values=c("grey50"))+xlab("Year")+
            geom_vline(aes(xintercept=2005),linetype=2)+
            geom_vline(aes(xintercept=2010),linetype=2)+
            geom_vline(aes(xintercept=2015),linetype=2)+
            theme(axis.title.y=element_blank(), axis.text.y=element_blank()),
            widths=c(1,0.8))
```

**Figure `r iFig=iFig+1;iFig`** 


```{r, boxplot}
fn<-function(x) {
  r=quantile(x, probs=c(0.05, 0.33, 0.5, 0.66, 0.95))
  names(r)=c("ymin", "lower", "middle", "upper", "ymax")
  r}
```


```{r}
load("../data/results/ts.RData")

ts=transform(ts,Period=cut(year,breaks=c(2004,2009,2019,2020)))
ICESStatus=ddply(ts,.(OM,SRR,Period),transmute, 
                 F=mean(F),Yield=mean(Catch),SSB=mean(SSB))
ICESStatus=subset(ICESStatus,!(OM=="Barents Sea"&(SRR=="Depensation"|SRR=="h=0.9"))&
                             !(OM=="North Sea"  &(SRR=="Depensation"|SRR=="h=0.9"))&
                              !OM=="M=0.15"&!OM=="High M")
ICESStatus=cbind(ICESStatus,Recruits="Historical\nRec. trend")
ICESStatus=transform(ICESStatus,OM =factor(OM,levels=c("Reference","North Sea", "Barents Sea")),
                                SRR=factor(SRR,levels=c("Prior","h=0.9","Depensation")))
```


```{r, boxplot-catch, fig.height=6, fig.width=8}
dat=as.data.frame(results$Catch,drop=T) 
dat=cbind(dat,scen[dat$qname,])
dat$Period=cut(dat$year,breaks=c(2004,2009,2019,2020))
dat=subset(dat,!is.na(Period))
dat=ddply(dat,.(OM,SRR,Recruits,Period), with, data.frame(data=filterLims(data)))
dat=transform(dat,OM      =factor(OM,      levels=c("Reference","North Sea", "Barents Sea")),
                  SRR     =factor(SRR,     levels=c("Prior","h=0.9","Depensation")),
                  Recruits=factor(Recruits,levels=c("AR","Regime"),labels=c("Random\nRec. trend","Historical\nRec. trend")))

bxC=ggplot(aes(x=Period,group=Period,qname,y=data),data=dat)+  
   geom_rect(aes(xmin=-Inf,xmax=Inf,ymin=0.8,ymax=1.0),fill="#009E73", alpha=0.3)+
   geom_rect(aes(xmin=-Inf,xmax=Inf,ymin=1.0,ymax=Inf),fill="#EE0000", alpha=0.3)+
   geom_rect(aes(xmin=-Inf,xmax=Inf,ymin=0.0,ymax=0.8),fill="#EE0000", alpha=0.3)+
   stat_summary(fun.data=fn, geom="boxplot")+  
   facet_grid(OM+SRR~Recruits)+
   theme_bw(12)+ 
   theme(legend.position="none",
        axis.title.x=element_text(colour='NA'), 
        axis.ticks=  element_line(colour="NA"))+
   #geom_hline(aes(yintercept=level,linetype=Regime),
   #                                   data=rfLn,col="darkgreen")+
   geom_hline(aes(yintercept=Yield, group=Period),
               linetype="solid",col="#E0FFFF",linewidth=1,data=ICESStatus)+
   scale_y_continuous(labels=percent, limits=c(0,2.5), breaks=c(1,2))+
   xlab("")+ylab("Difference from MSY Reference Level")+ 
   theme(#axis.title.y=element_blank(),
         axis.text.x =element_text(angle=45, hjust=1))+
   labs(subtitle="Catch") 

bxC
```

**Figure `r iFig=iFig+1;iFig`** Catch

```{r, boxplot-SSB, fig.height=6, fig.width=8}
dat=as.data.frame(results$SSB,drop=T) 
dat=cbind(dat,scen[dat$qname,])
dat$Period=cut(dat$year,breaks=c(2004,2009,2019,2020))
dat=subset(dat,!is.na(Period))
dat=ddply(dat,.(OM,SRR,Recruits,Period), with, data.frame(data=filterLims(data)))
dat=transform(dat,OM      =factor(OM,      levels=c("Reference","North Sea", "Barents Sea")),
                  SRR     =factor(SRR,     levels=c("Prior","h=0.9","Depensation")),
                  Recruits=factor(Recruits,levels=c("AR","Regime"),labels=c("Random\nRec. trend","Historical\nRec. trend")))

bxS=ggplot(aes(x=Period,group=Period,qname,y=data),data=dat)+  
   geom_rect(aes(xmin=-Inf,xmax=Inf,ymin=1.0,ymax=Inf),fill="#009E73", alpha=0.3)+
   geom_rect(aes(xmin=-Inf,xmax=Inf,ymin=0.0,ymax=1.0),fill="#EE0000", alpha=0.3)+
   stat_summary(fun.data=fn, geom="boxplot")+  
   facet_grid(OM+SRR~Recruits)+
   theme_bw(12)+ 
   theme(legend.position="none",
        axis.title.x=element_text(colour='NA'), 
        axis.ticks=  element_line(colour="NA"))+
   geom_hline(aes(yintercept=SSB),
                    linetype="solid",col="#E0FFFF",linewidth=1,data=ICESStatus )+
   #geom_hline(aes(yintercept=1),col="darkgreen")+
  #geom_hline(aes(yintercept=SSB),linetype=1,colour="darkred",data=vrgLn)+
   scale_y_continuous(labels=percent, limits=c(0,2.5), breaks=c(1,2))+
   xlab("")+ylab("Difference from BMSY Reference Level")+ 
   theme(#axis.title.y=element_blank(),
         axis.text.x =element_text(angle=45, hjust=1))+
   labs(subtitle=expression("Status"["SSB"]))

bxS
```

**Figure `r iFig=iFig+1;iFig`** SSB

```{r, boxplot-F, fig.height=6, fig.width=8}
dat=as.data.frame(results$F,drop=T) 
dat=cbind(dat,scen[dat$qname,])
dat$Period=cut(dat$year,breaks=c(2004,2009,2019,2020))
dat=subset(dat,!is.na(Period))
dat=ddply(dat,.(OM,SRR,Recruits,Period), with, data.frame(data=filterLims(data)))
dat=transform(dat,OM      =factor(OM,      levels=c("Reference","North Sea", "Barents Sea")),
                  SRR     =factor(SRR,     levels=c("Prior","h=0.9","Depensation")),
                  Recruits=factor(Recruits,levels=c("AR","Regime"),labels=c("Random\nRec. trend","Historical\nRec. trend")))

bxF=ggplot(aes(x=Period,group=Period,qname,y=data),data=dat)+  
   geom_rect(aes(xmin=-Inf,xmax=Inf,ymin=1.0,ymax=Inf),fill="#EE0000", alpha=0.3)+
   geom_rect(aes(xmin=-Inf,xmax=Inf,ymin=0.0,ymax=1.0),fill="#009E73", alpha=0.3)+
   stat_summary(fun.data=fn, geom="boxplot")+  
   facet_grid(OM+SRR~Recruits,scales="free",space="free")+
   theme_bw(12)+ 
   theme(legend.position="none",
        axis.title.x=element_text(colour='NA'), 
        axis.ticks=  element_line(colour="NA"))+
   scale_y_continuous(labels=percent, limits=c(0,2.5), breaks=c(1,2))+
   geom_hline(aes(yintercept=F),
                     linetype="solid",col="#E0FFFF",linewidth=1,data=ICESStatus )+
   #geom_hline(aes(yintercept=1),col="darkgreen")+
   xlab("")+ylab("Difference from FMSY Reference Level")+ 
   theme(#axis.title.y=element_blank(),
         axis.text.x =element_text(angle=45, hjust=1))+
   labs(subtitle=expression("Status"["F"]))

bxF
```

**Figure `r iFig=iFig+1;iFig`** F


```{r, boxplot-Recruits, fig.height=6, fig.width=8}
dat=as.data.frame(results$Recruits,drop=T) 
dat=cbind(dat,scen[dat$qname,])
dat$Period=cut(dat$year,breaks=c(2004,2009,2019,2020))
dat=subset(dat,!is.na(Period))
dat=ddply(dat,.(OM,SRR,Recruits,Period), with, data.frame(data=filterLims(data)))
dat=transform(dat,OM      =factor(OM,      levels=c("Reference","North Sea", "Barents Sea")),
                  SRR     =factor(SRR,     levels=c("Prior","h=0.9","Depensation")),
                  Recruits=factor(Recruits,levels=c("AR","Regime"),labels=c("Random\nRec. trend","Historical\nRec. trend")))

bxR=ggplot(aes(x=Period,group=Period,qname,y=data),data=dat)+  
   stat_summary(fun.data=fn, geom="boxplot")+  
   facet_grid(OM+SRR~Recruits)+
   theme_bw(12)+ 
   theme(legend.position="none",
        axis.title.x=element_text(colour='NA'), 
        axis.ticks=  element_line(colour="NA"))+
   #geom_hline(aes(yintercept=level,linetype=Regime),
   #                                 data=rfLn,col="darkgreen")+
   #geom_hline(aes(yintercept=Recruits),linetype=1,colour="darkred",data=vrgLn)+
   scale_y_continuous(labels=percent)+
   xlab("")+ylab("Difference from RMSY Reference Level")+ 
   theme(#axis.title.y=element_blank(),
         axis.text.x =element_text(angle=45, hjust=1))+
   labs(subtitle="Recruits")

bxR
```

**Figure `r iFig=iFig+1;iFig`** Recruits


```{r, boxplot-BRebuild, fig.height=6, fig.width=8}
load("../data/results/results.RData")
dat=as.data.frame(mcf(results$Rebuild),drop=T) 
dat$qname=gsub("h=0\\.9","High h",dat$qname)
dat=dat %>% separate(qname, into=c("OM", "SRR", "Recruits"), sep="\\.")

dat$Period=cut(dat$year,breaks=c(2004,2009,2019,2020))
dat=subset(dat,!is.na(Period))
dat=ddply(dat,.(OM,SRR,Recruits,Period), with, data.frame(data=filterLims(data)))
dat=transform(dat,OM      =factor(OM,      levels=c("Reference","North Sea", "Barents Sea")),
                  SRR     =factor(SRR,     levels=c("Prior","h=0.9","Depensation")),
                  Recruits=factor(Recruits,levels=c("Regime","AR"),
                                           labels=c("Historical\nRec. trend","Random\nRec. trend")))
gt=transform(gt,OM =factor(OM,levels=c("Reference","North Sea", "Barents Sea")),
                           SRR=factor(SRR,levels=c("Prior","h=0.9","Depensation")))

bxBr=ggplot(aes(x=Period,group=Period,qname,y=data),data=dat)+  
   stat_summary(fun.data=fn, geom="boxplot")+  
   facet_grid(OM+SRR~Recruits)+
   theme_bw(12)+ 
   theme(legend.position="none",
        axis.title.x=element_text(colour='NA'), 
        axis.ticks=  element_line(colour="NA"))+
   geom_hline(aes(yintercept=0), col="darkgreen",linewidth=1)+
   geom_hline(aes(yintercept=gt),col="darkred",linewidth=1,data=gt)+
   scale_y_continuous(breaks=c(-10,0,10))+
   xlab("")+ylab(expression("Years to B"["MSY"]))+ 
   theme(#axis.title.y=element_blank(),
         axis.text.x =element_text(angle=45, hjust=1))+
   labs(subtitle="BRebuild")

bxBr
```

**Figure `r iFig=iFig+1;iFig`** BRebuild

```{r, boxplot-Forage, fig.height=6, fig.width=8}
dat=as.data.frame(results$Forage,drop=T) 
dat=cbind(dat,scen[dat$qname,])
dat$Period=cut(dat$year,breaks=c(2004,2009,2019,2020))
dat=subset(dat,!is.na(Period))
dat=ddply(dat,.(OM,SRR,Recruits,Period), with, data.frame(data=filterLims(data)))
dat=transform(dat,OM      =factor(OM,      levels=c("Reference","North Sea", "Barents Sea")),
                  SRR     =factor(SRR,     levels=c("Prior","h=0.9","Depensation")),
                  Recruits=factor(Recruits,levels=c("Regime","AR"),
                                           labels=c("Historical\nRec. trend","Random\nRec. trend")))

bxFr=ggplot(aes(x=Period,group=Period,qname,y=data),data=dat)+  
   stat_summary(fun.data=fn, geom="boxplot")+  
   facet_grid(OM+SRR~Recruits,scales="free",space="free")+
   theme_bw(12)+ 
   theme(legend.position="none",
        axis.title.x=element_text(colour='NA'), 
        axis.ticks=  element_line(colour="NA"))+
   geom_hline(aes(yintercept=1),  col="darkgreen",linewidth=1)+
   geom_hline(aes(yintercept=0.5),col="darkred",  linewidth=1)+
   scale_y_continuous(labels=percent, breaks=c(1,2))+
   xlab("")+ylab("Difference from MSY Reference Level")+ 
   theme(#axis.title.y=element_blank(),
         axis.text.x =element_text(angle=45, hjust=1))+
   labs(subtitle="Forage")

bxFr
```

**Figure `r iFig=iFig+1;iFig`** Forage


```{r, rfvg}
vg=data.frame(ref=unlist(c(vrgLn[1,3:5])),qname=names(vrgLn[,3:5])) 

rf=data.frame(ref=rfLn[2,2],qname=c("Forage","SSB","Recruits"))
```


```{r, boxplot-ABI, fig.height=6, fig.width=8}
dat=as.data.frame(FLQuants(results$ABI),drop=T) 
dat=cbind(dat,scen[dat$qname,])
dat$Period=cut(dat$year,breaks=c(2004,2009,2019,2020))
dat=subset(dat,!is.na(Period))
dat=ddply(dat,.(OM,SRR,Recruits,Period), with, data.frame(data=filterLims(data)))
dat=transform(dat,OM      =factor(OM,      levels=c("Reference","North Sea", "Barents Sea")),
                  SRR     =factor(SRR,     levels=c("Prior","h=0.9","Depensation")),
                  Recruits=factor(Recruits,levels=c("Regime","AR"),
                                           labels=c("Historical\nRec. trend","Random\nRec. trend")))

bxA=ggplot(aes(x=Period,group=Period,qname,y=data),data=dat)+  
   stat_summary(fun.data=fn, geom="boxplot")+  
   facet_grid(OM+SRR~Recruits)+
   theme_bw(12)+ 
   theme(legend.position="none",
        axis.title.x=element_text(colour='NA'), 
        axis.ticks=  element_line(colour="NA"))+
   geom_hline(aes(yintercept=1),  col="darkgreen",linewidth=1)+
   geom_hline(aes(yintercept=0.5),col="darkred"  ,linewidth=1)+
   scale_y_continuous(labels=percent,breaks=c(1,3))+
   xlab("")+ylab("Difference from MSY Reference Level")+ 
   theme(#axis.title.y=element_blank(),
         axis.text.x =element_text(angle=45, hjust=1))+
   labs(title=expression("ABI"["MSY"]))

bxA
```

**Figure `r iFig=iFig+1;iFig`** ABI

```{r, bx1, fig.height=14, fig.width=12}
p1 =ggarrange(bxS,bxF,bxC,  ncol=3,nrow=1,common.legend=TRUE)

ggsave("fig6a.png", p1, width=12, height=8, dpi=300) 
```

```{r, bx2, fig.height=14, fig.width=12}
p2 =ggarrange(bxBr,bxA,bxFr,ncol=3,nrow=1,common.legend=TRUE)
ggsave("fig6b.png", p2, width=12, height=8, dpi=300) 
```

```{r, bxs, fig.height=14, fig.width=12}
p12=ggarrange(bxS,bxF,bxC,bxBr,bxA,bxFr,ncol=3,nrow=2,common.legend=TRUE) 
p12 
```


```{r, ABI, fig.height=6, fig.width=8}
for (i in seq(dim(scen)[1])){
  refpts(eqs[[scen[i,"OM"]]][[scen[i,"SRR"]]])["msy",
            c("ssb","rec","yield","harvest")]=
    unlist(c(subset(msy,OM==scen[i,"OM"]&SRR==scen[i,"SRR"])[,3:6]))}


for (i in seq(dim(scen)[1])){
  refpts(eqs[[scen[i,"OM"]]][[scen[i,"SRR"]]])["msy",
            c("ssb","rec","yield","harvest")]=
    unlist(c(subset(msy,OM==scen[i,"OM"]&SRR==scen[i,"SRR"])[,3:6]))}

abi=mlply(seq(10), function(.id) 
  ABI(robustness[[.id]],eqs[[scen[.id,"OM"]]][[scen[.id,"SRR"]]]))

plot(FLQuants(abi))+geom_hline(aes(yintercept=1))
```

**Figure `r iFig=iFig+1;iFig`** ABI 

```{r, rbld, eval=FALSE}
load("../data/om/robustnessEq.RData")

rebuildInterp<-function(x,y,new){
  f=splinefun(x, y)
  f(new)} 

scen=data.frame(OM =c(rep("Reference",3),"Barents Sea","North Sea"),
                SRR=c("Prior","h=0.9","Depensation","Prior","Prior"))

rbt=mdply(scen, function(OM,SRR) {
             eq   =eqs[[OM]][[SRR]]
             rb   =FLCandy:::tryIt(rebuild(eq))
             r2   =FLCandy:::tryIt(rebuildTime(rb))
             FLCandy:::tryIt(return(cbind(r2,gt=c(gt(eq)))))})
             
rbt2=ddply(rbt, .(OM,SRR), with, rebuildInterp(initial,year,ssb(oms[[OM[1]]][[SRR[1]]])))


ggplot(subset(rb2,!is.na(year)))+geom_line(aes(initial,year))

rebuildInterp(rb2$initial,rb2$year,.5)
  
ggplot(rbt)+
  geom_line(aes(Year,Initial,col=SRR))+
  geom_vline(aes(xintercept=V1),data=gtime)+
  facet_grid(factor(OM,levels=c("Reference","High M",
                                "Environmental\nDriver"))~.)+
  #coord_cartesian(xlim=c(0,12))+
  xlab("Time to recovery to BMSY")+ylab("Initial Depletion (SSB/Bmsy)")
  
x=FLCandy:::rebuild(eqs[["Reference"]][["Prior"]],n=201)
y=FLCandy:::rebuildTime(eqs[["Reference"]][["Prior"]])

rcv =FLCandy:::rebuild(eq,n=201)
rcv2=FLCandy:::rebuildTime(rcv)
brbl=FLQuant(FLCandy:::rebuildInterp(rcv[,1],rcv[,2],
                           ssb(reference[["Short Cut"]])%/%refpts(eq)["msy","ssb"]),
             dimnames=dimnames(ssb(reference[["Short Cut"]])))
eq=eqs[[1]][[1]]

bmsy=refpts(eq)["msy","ssb"] #ssb(eq)[,dimnames(catch(eq))$year[c(catch(eq))==max(catch(eq))]]

rcv =llply(eqs, function(x) 
        llply(x,function(x) FLCandy:::rebuildTime(x,
            FLCandy:::rebuild(x,n=201))))
                            
brbl=FLQuant(FLCandy:::rebuildInterp(rcv[,1],rcv[,2],
                             ssb(x)%/%bmsy),
               dimnames=dimnames(ssb(x)))
```

```{r, ts2}
load("../data/results/results.RData") 

myColours=c(
  "reference"="#4e9a5b",
  "target"   ="#4e9a5b",
  "limit"    ="#b03a3a",
  "main"     ="#2c3e50")

rectFills=list(
  list(xmax=2020, fill="#E0FFFF"),
  list(xmax=2018, fill="#AFEEEE"),
  list(xmax=2010, fill="#90D5FF"))

p1=plot(FLQuants(map(results, ~ .x[[1]])),iter=23)+
  geom_rect(aes(xmin=-Inf,xmax=2020,ymin=-Inf,ymax=Inf),fill="#E0FFFF",alpha=0.1)+
  geom_rect(aes(xmin=-Inf,xmax=2018,ymin=-Inf,ymax=Inf),fill="#AFEEEE",alpha=0.1)+
  geom_rect(aes(xmin=-Inf,xmax=2010,ymin=-Inf,ymax=Inf),fill="#90D5FF",alpha=0.1)+
  labs(title="b) Historical recruitment trend (Epistemic)") +
  facet_grid(factor(qname, levels=c( "Recruits", "F", "SSB", "Catch","Forage", "ABI","Rebuild")) ~ ., 
           scales="free_y") +
  geom_hline(aes(yintercept=1),   col="grey40", linewidth=0.5) +
  geom_hline(aes(yintercept=ref), col=myColours["target"],linewidth=0.5, data=rf) +
  geom_hline(aes(yintercept=ref), col=myColours["limit"], linewidth=0.5, data=vg) +
  scale_colour_manual(values=myColours["main"]) +
  scale_x_continuous(limits=c(1995, 2020), breaks=seq(2000, 2020, 10),expand=c(0, 0)) +
  xlab("Year") +
  theme_bw(base_size=12) +
  theme(
  strip.text.y=element_text(angle=0, hjust=0, size=11, face="bold"),
  strip.background=element_rect(fill="grey95", color="grey80"),
  panel.grid.minor=element_blank(),
  panel.grid.major.x=element_line(color="grey90", size=0.5),
  panel.grid.major.y=element_line(color="grey90", size=0.5),
  legend.position="none",
  plot.title=element_text(size=14, face="bold", margin=margin(b=10)),
  axis.title.x=element_text(size=11, margin=margin(t=8)),
  axis.title.y=element_text(size=11, margin=margin(r=8)),
  panel.spacing.y=unit(0.3, "cm"))+ 
  facetted_pos_scales(y=list(
    scale_y_continuous(limits=c(0, 3),expand=c(0, 0)),
    scale_y_continuous(limits=c(0, 3),expand=c(0, 0)),
    scale_y_continuous(limits=c(0, 3),expand=c(0, 0)),
    scale_y_continuous(limits=c(0, 3),expand=c(0, 0)),
    scale_y_continuous(limits=c(0, 3),expand=c(0, 0)),
    scale_y_continuous(limits=c(0, 3),expand=c(0, 0)),
    scale_y_continuous(limits=c(-10,10))))

p1$layers
p1$layers[[3]]$aes_params$alpha=1.0
p1$layers[[3]]$aes_params$fill="pink" 
p1$layers[[1]]$aes_params$fill="orchid"
p1$layers=c(p1$layers[c(6,7,8,3,1)],p1$layers[-c(6,7,8,3,1)])

p2=plot(FLQuants(map(results, ~ .x[[6]])), iter=23) +
  lapply(rectFills, function(r) {
    geom_rect(aes(xmin=-Inf, xmax=r$xmax, ymin=-Inf, ymax=Inf),
             fill=r$fill, alpha=0.1)}) +
  labs(title="b) Historical recruitment trend (Epistemic)") +
  facet_grid(factor(qname, levels=c("Recruits", "F", "SSB", "Catch", "Forage", "ABI", "Rebuild")) ~ .,
           scales="free_y") +
  geom_hline(aes(yintercept=1), col="grey40", linewidth=0.5) +
  geom_hline(aes(yintercept=ref), col=myColours["target"], linewidth=0.5, data=rf) +
  geom_hline(aes(yintercept=ref), col=myColours["limit"], linewidth=0.5, data=vg) +
  # Scales and coordinates
  scale_colour_manual(values=myColours["main"]) +
  scale_x_continuous(
    limits=c(1995, 2020),
    breaks=seq(2000, 2020, 10),
    expand=c(0, 0))+
  xlab("Year") +
  theme_bw(base_size=12) +
  theme(
    strip.text.y=element_text(angle=0, hjust=0, size=11, face="bold"),
    strip.background=element_rect(fill="grey95", color="grey80"),
    panel.grid.minor=element_blank(),
    panel.grid.major=element_line(color="grey90", linewidth=0.5),
    legend.position="none",
    plot.title=element_text(size=14, face="bold", margin=margin(b=10)),
    axis.title=element_text(size=11, margin=margin(t=8, r=8)),
    panel.spacing.y=unit(0.3, "cm"))+
  facetted_pos_scales(y=c(
    rep(list(scale_y_continuous(limits=c(0, 3), expand=c(0, 0))), 6),
    list(scale_y_continuous(limits=c(-10, 10)))))

# Modify layer aesthetics
p2$layers[[3]]$aes_params$alpha=1.0   
p2$layers[[3]]$aes_params$fill="pink" 
p2$layers[[1]]$aes_params$fill="orchid"
p2$layers=c(p2$layers[c(6,7,8,3,1)], p2$layers[-c(6,7,8,3,1)])

combinedPlot=p2+p1+ 
  plot_layout(ncol=2) +
  plot_annotation(
    caption="Dashed green line: Target, Red line: Limit")

combinedPlot

ggsave("fig4.png", combinedPlot, width=12, height=8, dpi=300)
```


```{r, fig.height=10,gig.width=12}
dtS=mdply("SSB", function(x) cbind(what=x,ldply(results[[x]], 
                              function(x) as.data.frame(FLQuants(x[,ac(2004:2020)]),drop=T)))) 
dtS=cbind(dtS,scen[dtS$.id,])[,-c(1,3,7)]
dtS$Period=cut(dtS$year,breaks=c(2003,2009,2019,2020))

dtF=mdply("F", function(x) cbind(what=x,ldply(results[[x]], 
                              function(x) as.data.frame(FLQuants(x[,ac(2004:2020)]),drop=T)))) 
dtF=cbind(dtF,scen[dtF$.id,])[,-c(1,3,7)]
dtF$Period=cut(dtF$year,breaks=c(2003,2009,2019,2020))

dtK=merge(dtS[,-1],dtF[,-c(1,8)],by=names(dtS)[c(2:3,5:7)])
names(dtK)[6]="stock" 
names(dtK)[8]="harvest"

dtK=mutate(dtK,kobe:::prob(stock,harvest),
               orange=as.numeric((overFishing==1&overFished==0)),
               yellow=yellow-orange)
dtK=transform(dtK,OM      =factor(OM,      levels=c("Reference","North Sea", "Barents Sea")),
                  SRR     =factor(SRR,     levels=c("Prior","h=0.9","Depensation")),
                  Recruits=factor(Recruits,levels=c("AR","Regime"),
                                           labels=c("Random\nRec. trend","Historical\nRec. trend")))

dtK=ddply(dtK,.(year,OM,SRR,Recruits),with, 
      data.frame(red   =mean(red),
                 green =mean(green),
                 yellow=mean(yellow),
                 orange=mean(orange)))
p1=ggplot(dtK)+
  geom_ribbon(aes(year,ymin=0,ymax=red),fill="red")+
  geom_ribbon(aes(year,ymin=red,ymax=red+yellow),fill="yellow")+
  geom_ribbon(aes(year,ymin=red+yellow,ymax=red+yellow+orange),fill="orange")+
  geom_ribbon(aes(year,ymin=red+yellow+orange,ymax=1),fill="green")+
  facet_nested(OM+SRR~Recruits,
               scale="free", nest_line=TRUE, solo_line=TRUE,labeller=label_wrap_gen(width=10))+
  xlab("Year")+
  ylab("P()")
p1

ggsave("fig5.png", p1, width=10, height=10, dpi=300) 
```

```{r, targets, fig.height=4,gig.width=6}
tarS=ddply(dtS, .(Period,OM,SRR,Recruits), with, cut(ecdf(data)(1),breaks=c(0,0.66,0.5,1)))
tarS=transform(tarS,OM      =factor(OM,      levels=c("Reference","North Sea", "Barents Sea")),
                  SRR     =factor(SRR,     levels=c("Prior","h=0.9","Depensation")),
                  Recruits=factor(Recruits,levels=c("Regime","AR"),
                                           labels=c("Historical\nRec. trend","Random\nRec. trend")))
ggplot(tarS)+
  geom_point(aes(Period,1,col=V1),size=5)+
  facet_grid(OM+SRR~Recruits)+
  scale_color_manual(values=c("darkgreen","gold","red"))+
  theme(#axis.title.y=element_blank(),
         axis.text.x =element_text(angle=45, hjust=1))

tarS =merge(tarS, data.frame(V1=unique(tarS$V1), colour=c("red","gold","green")))
```

```{r, fig.height=4,gig.width=6}
tarF=ddply(dtF, .(Period,OM,SRR,Recruits), with, cut(ecdf(data)(1),breaks=c(0,0.33,0.5,1)))
tarF=transform(tarF,OM    =factor(OM,      levels=c("Reference","North Sea", "Barents Sea")),
                  SRR     =factor(SRR,     levels=c("Prior","h=0.9","Depensation")),
                  Recruits=factor(Recruits,levels=c("Regime","AR"),
                                           labels=c("Historical\nRec. trend","Random\nRec. trend")))
ggplot(tarF)+
  geom_point(aes(Period,1,col=V1),size=5)+
  facet_grid(OM+SRR~Recruits)+
  scale_color_manual(values=c("red","gold","darkgreen"))+
  theme(#axis.title.y=element_blank(),
         axis.text.x =element_text(angle=45, hjust=1))

tarF =merge(tarF, data.frame(V1=unique(tarF$V1), colour=c("gold","green","red")))
```

```{r, fig.height=4,gig.width=6}
dtY=mdply("Catch", function(x) cbind(what=x,ldply(results[[x]], 
                              function(x) as.data.frame(FLQuants(x[,ac(2004:2020)]),drop=T)))) 
dtY=cbind(dtY,scen[dtY$.id,])[,-c(1,3,7)]
dtY$Period=cut(dtY$year,breaks=c(2003,2009,2019,2020))
tarY=ddply(dtY, .(Period,OM,SRR,Recruits), with, cut(median(data),breaks=c(0,0.8,1,10)))
tarY=transform(tarY,OM      =factor(OM,      levels=c("Reference","North Sea", "Barents Sea")),
                    SRR     =factor(SRR,     levels=c("Prior","h=0.9","Depensation")),
                    Recruits=factor(Recruits,levels=c("Regime","AR"),
                                             labels=c("Historical\nRec. trend","Random\nRec. trend")))
ggplot(tarY)+
  geom_point(aes(Period,1,col=V1),size=5)+
  facet_grid(OM+SRR~Recruits)+
  scale_color_manual(values=c("gold","darkgreen","red"))+
  theme(#axis.title.y=element_blank(),
         axis.text.x =element_text(angle=45, hjust=1))

tarY =merge(tarY, data.frame(V1=unique(tarY$V1), colour=c("gold","green","red")))
```

```{r, fig.height=4,gig.width=6}
library(tidyr)

load("../data/results/results.RData")

dtB=mdply(names(results["Rebuild"]), function(x) cbind(what=x,ldply(results[[x]], 
                  function(x) as.data.frame(FLQuants(x[,ac(2004:2020)]),drop=T))))[,-c(1,7)]
dtB$.id=gsub("h=0\\.9","High h",dtB$.id)
dtB=dtB %>% separate(.id, into=c("OM", "SRR", "Recruits"), sep="\\.")
dtB$Period=cut(dtB$year,breaks=c(2003,2009,2019,2020))
erpB=ddply(dtB, .(Period,OM,SRR,Recruits), with, cut(ecdf(data)(0),breaks=c(0,0.33,0.5,1)))  
erpB=transform(erpB,OM    =factor(OM,      levels=c("Reference","North Sea", "Barents Sea")),
                  SRR     =factor(SRR,     levels=c("Prior","High h","Depensation")),
                  Recruits=factor(Recruits,levels=c("Regime","AR"),
                                           labels=c("Historical\nRec. trend","Random\nRec. trend")))

ggplot(erpB)+
  geom_point(aes(Period,1,col=V1),size=5)+
  facet_grid(OM+SRR~Recruits)+
  scale_color_manual(values=c("red","gold","darkgreen"))+
  theme(#axis.title.y=element_blank(),
         axis.text.x =element_text(angle=45, hjust=1))
 
erpB =merge(erpB, data.frame(V1=unique(erpB$V1),colour=c("green","gold","red")))
```

```{r, fig.height=4,gig.width=6}
dtA=mdply(names(results["ABI"]), function(x) cbind(what=x,ldply(results[[x]], 
                  function(x) as.data.frame(FLQuants(x[,ac(2004:2020)]),drop=T))))
dtA=cbind(dtA,scen[dtA$X1,])[,-c(1:2,6)]
dtA$Period=cut(dtA$year,breaks=c(2003,2009,2019,2020))
erpA=ddply(dtA, .(Period,OM,SRR,Recruits), with, cut(ecdf(data)(1),breaks=c(0,0.66,0.5,1)))
erpA=transform(erpA,OM      =factor(OM,      levels=c("Reference","North Sea", "Barents Sea")),
                  SRR     =factor(SRR,     levels=c("Prior","h=0.9","Depensation")),
                  Recruits=factor(Recruits,levels=c("Regime","AR"),
                                           labels=c("Historical\nRec. trend","Random\nRec. trend")))
ggplot(erpA)+
  geom_point(aes(Period,1,col=V1),size=5)+
  facet_grid(OM+SRR~Recruits)+
  scale_color_manual(values=c("darkgreen","gold","red"))+
  theme(#axis.title.y=element_blank(),
         axis.text.x =element_text(angle=45, hjust=1))

erpA =merge(erpA, data.frame(V1=unique(erpA$V1), colour=c("green","gold","red")))
```

```{r, fig.height=4,gig.width=6}
dtFr=mdply(names(results["Forage"]), function(x) cbind(what=x,ldply(results[[x]], 
                  function(x) as.data.frame(FLQuants(x[,ac(2004:2020)]),drop=T))))
dtFr=cbind(dtFr,scen[dtFr$.id,])[,-c(1:3,7)]
dtFr$Period=cut(dtFr$year,breaks=c(2003,2009,2019,2020))
erpFr=ddply(dtFr, .(Period,OM,SRR,Recruits), with, cut(ecdf(data)(1),breaks=c(0,0.66,0.5,1)))
erpFr=transform(erpFr,OM      =factor(OM,      levels=c("Reference","North Sea", "Barents Sea")),
                    SRR     =factor(SRR,     levels=c("Prior","h=0.9","Depensation")),
                    Recruits=factor(Recruits,levels=c("Regime","AR"),
                                             labels=c("Historical\nRec. trend","Random\nRec. trend")))
ggplot(erpFr)+
  geom_point(aes(Period,1,col=V1),size=5)+
  facet_grid(OM+SRR~Recruits)+
  scale_color_manual(values=c("darkgreen","gold","red"))+
  theme(#axis.title.y=element_blank(),
         axis.text.x =element_text(angle=45, hjust=1))

erpFr=merge(erpFr,data.frame(V1=unique(erpFr$V1),colour=c("green","gold","red")))
```


```{r, limits, fig.height=4,gig.width=6}
dtA=mdply(names(results["ABI"]), function(x) cbind(what=x,ldply(results[[x]], 
                  function(x) as.data.frame(FLQuants(x[,ac(2004:2020)]),drop=T))))
dtA=cbind(dtA,scen[dtA$X1,])[,-c(1:2,6)]
dtA$Period=cut(dtA$year,breaks=c(2003,2009,2019,2020))
limA=ddply(dtA, .(Period,OM,SRR,Recruits), with, cut(ecdf(data)(0.5),breaks=c(-0.1,0.05,1)))
limA=transform(limA,OM      =factor(OM,      levels=c("Reference","North Sea", "Barents Sea")),
                  SRR     =factor(SRR,     levels=c("Prior","h=0.9","Depensation")),
                  Recruits=factor(Recruits,levels=c("Regime","AR"),
                                           labels=c("Historical\nRec. trend","Random\nRec. trend")))
ggplot(limA)+
  geom_point(aes(Period,1,col=V1),size=5)+
  facet_grid(OM+SRR~Recruits)+
  scale_color_manual(values=c("darkgreen","red"))+
  theme(#axis.title.y=element_blank(),
         axis.text.x =element_text(angle=45, hjust=1))

limA =merge(limA, data.frame(V1=unique(limA$V1), colour=c("red","green")))
```

```{r, fig.height=4,gig.width=6}
dtFr=mdply(names(results["Forage"]), function(x) cbind(what=x,ldply(results[[x]], 
                  function(x) as.data.frame(FLQuants(x[,ac(2004:2020)]),drop=T))))
dtFr=cbind(dtFr,scen[dtFr$.id,])[,-c(1:3,7)]
dtFr$Period=cut(dtFr$year,breaks=c(2003,2009,2019,2020))
limFr=ddply(dtFr, .(Period,OM,SRR,Recruits), with, cut(ecdf(data)(0.5),breaks=c(-1,0.05,1)))
limFr=transform(limFr,OM      =factor(OM,      levels=c("Reference","North Sea", "Barents Sea")),
                    SRR     =factor(SRR,     levels=c("Prior","h=0.9","Depensation")),                                      Recruits=factor(Recruits,levels=c("Regime","AR"),
                                             labels=c("Historical\nRec. trend","Random\nRec. trend")))
ggplot(limFr)+
  geom_point(aes(Period,1,col=V1),size=5)+
  facet_grid(OM+SRR~Recruits)+
  scale_color_manual(values=c("darkgreen","red"))+
  theme(#axis.title.y=element_blank(),
         axis.text.x =element_text(angle=45, hjust=1))

limFr=merge(limFr,data.frame(V1=unique(limFr$V1),colour=c("red","green")))
```

```{r, fig.height=4,gig.width=6}
library(tidyr)

load("../data/results/results.RData")

dtB=mdply(names(results["Rebuild"]), function(x) cbind(what=x,ldply(results[[x]], 
                  function(x) as.data.frame(FLQuants(x[,ac(2004:2020)]),drop=T))))[,-c(1,7)]
dtB$.id=gsub("h=0\\.9","High h",dtB$.id)

dtB=dtB %>% separate(.id, into=c("OM", "SRR", "Recruits"), sep="\\.")
dtB$Period=cut(dtB$year,breaks=c(2003,2009,2019,2020))
limB=ddply(dtB, .(Period,OM,SRR,Recruits), with, cut(ecdf(data/8.5)(1),breaks=c(0,0.95,1)))
limB=transform(limB,OM      =factor(OM,      levels=c("Reference","North Sea", "Barents Sea")),
                    SRR     =factor(SRR,     levels=c("Prior","High h","Depensation")),
                    Recruits=factor(Recruits,levels=c("Regime","AR"),
                                             labels=c("Historical\nRec. trend","Random\nRec. trend")))
ggplot(limB)+
  geom_point(aes(Period,1,col=V1),size=5)+
  facet_grid(OM+SRR~Recruits)+
  scale_color_manual(values=c("red","darkgreen"))+
  theme(#axis.title.y=element_blank(),
         axis.text.x =element_text(angle=45, hjust=1))

limB =merge(limB, data.frame(V1=unique(limB$V1), colour=c("green","red")))
```


```{r}
tar=rbind(cbind(What="Target",rbind(
          cbind(Ref="SSB",  tarS), 
          cbind(Ref="F",    tarF), 
          cbind(Ref="Yield",tarY))))

erp=rbind(cbind(What="ERP Target",rbind(
          cbind(Ref="ABI",    erpA),
          cbind(Ref="Rebuild",erpB),  
          cbind(Ref="Forage", erpFr)))) 

lim=rbind(cbind(What="ERP Limit",rbind(
          cbind(Ref="ABI",    limA),
          cbind(Ref="Rebuild",limB), 
          cbind(Ref="Forage", limFr))))
```

```{r,fig.height=8,fig.width=12}
save(tar,erp,lim,file="C:/active/tmp/t.RData")
load("C:/active/tmp/t.RData")  

refs=rbind(cbind(Group="Target",    tar), 
           cbind(Group="Target ERP",erp),
           cbind(Group="Limit ERP", lim))
refs$SRR=gsub("h=0\\.9","High h",refs$SRR) 

refs$Ref=factor(refs$Ref,levels=c("SSB","F","Yield","ABI","Forage","Rebuild"))
save(tar,erp,lim,refs,file="C:/active/tmp/t.RData") 

refs$What=factor(refs$What,levels=c("Target","ERP Target","ERP Limit"))

p1=ggplot(refs)+
  geom_point(aes(Ref,1,colour=colour),size=8)+
  #facet_grid(Recruits+OM+SRR~Period)+
  facet_nested(Recruits+OM+SRR~Period+What,
               scale="free", nest_line=TRUE, solo_line=TRUE,labeller=label_wrap_gen(width=32))+
  theme(legend.position="bottom",
        axis.text.y=element_blank(), 
        axis.ticks.y=element_blank(),
        axis.title.y=element_blank(), 
        axis.text.x=element_text(angle=45, hjust=1))+
  scale_color_manual(values=c("gold","green","red"))
p1

ggsave("fig7.png", p1, width=10, height=12, dpi=300) 
```

**Figure `r iFig=iFig+1;iFig`** SHiT plot 


## Draft for Supplementary Materials: Explanation of Colour Derivation in Figure 17 (SHiT Plot)

The SHiT plot (Figure 17) presents a traffic-light style visual summary of the performance of multiple reference points across scenarios, periods, and recruitment regimes. The colours—green, gold, and red—indicate the probability that each indicator meets or exceeds its management target or falls below its limit, thereby providing an intuitive assessment of stock and ecosystem status.

### Data Preparation and Probability Calculation

For each performance metric (SSB, F, Yield, ABI, Forage, Rebuild), simulated values were extracted from the Operating Model (OM) outputs for each combination of scenario, period, and recruitment regime. The data were grouped accordingly, and empirical cumulative distribution functions (ecdf) were computed to estimate the probability that the metric met or exceeded a predefined reference level.

- For metrics where *higher values are better* (e.g., SSB, ABI, Forage), the probability was calculated as \$ P(X \geq reference) = 1 - ecdf(reference) \$.
- For metrics where *lower values are better* (e.g., fishing mortality F), the probability was calculated as \$ P(X \leq reference) = ecdf(reference) \$.
- For Yield, the median value relative to the reference was used instead of a probability.


### Breakpoints and Categorization

Probabilities or median values were binned into three categories corresponding to management status:


| Metric | Breakpoints (cut points) | Interpretation of Categories |
| :-- | :-- | :-- |
| SSB | $c(0, 0.5, 0.66, 1)$ | Red (<0.5), Gold (0.5–0.66), Green (>0.66) |
| F | $c(0, 0.33, 0.5, 1)$ | Red (<0.33), Gold (0.33–0.5), Green (>0.5) (Note: low F is better) |
| Yield | $c(0, 0.8, 1, 10)$ (median relative to ref) | Red (<0.8), Gold (0.8–1), Green (>1) |
| ABI | $c(0, 0.5, 0.66, 1)$ | Same as SSB |
| Forage | $c(0, 0.5, 0.66, 1)$ | Same as SSB |
| Rebuild | $c(0, 0.95, 1)$ | Red (<0.95), Green (≥0.95) (two categories only) |

These breakpoints were chosen to reflect management risk tolerances and provide meaningful distinctions between poor, cautionary, and good performance.

### Colour Mapping

Each category was assigned a colour for plotting:

- **Green:** High probability of meeting or exceeding the target (good status)
- **Gold:** Intermediate probability (cautionary status)
- **Red:** Low probability or failure to meet the target (poor status)

The colour assignments were merged with the categorized data and used in the ggplot2 plotting call to colour the points accordingly.

### Implementation in R

The categorization and colour assignment were implemented using `cut()` on the ecdf results or median values, followed by merging with a lookup table of colours. For example, for SSB:

```r
tarS = ddply(dtS, .(Period,OM,SRR,Recruits), with, cut(ecdf(data)(1), breaks=c(0,0.5,0.66,1)))
tarS = merge(tarS, data.frame(V1=unique(tarS$V1), colour=c("red","gold","green")))
```

Similar code blocks were used for other metrics with metric-specific breakpoints.

### Summary Table of Breakpoints and Colour Assignments

| Metric | Probability or Median Used | Breakpoints | Colours (Low to High) |
| :-- | :-- | :-- | :-- |
| SSB | Probability $P(X \geq 1)$ | 0–0.5, 0.5–0.66, 0.66–1 | Red, Gold, Green |
| F | Probability $P(X \leq 1)$ | 0–0.33, 0.33–0.5, 0.5–1 | Red, Gold, Green |
| Yield | Median relative to reference | 0–0.8, 0.8–1, >1 | Red, Gold, Green |
| ABI | Probability $P(X \geq 1)$ | Same as SSB | Red, Gold, Green |
| Forage | Probability $P(X \geq 1)$ | Same as SSB | Red, Gold, Green |
| Rebuild | Probability $P(\text{years} \leq 8.5)$ | 0–0.95, 0.95–1 | Red, Green (no gold) |

This approach provides a transparent, probabilistic basis for the traffic-light colours, facilitating rapid interpretation of complex simulation outcomes in the SHiT plot.


[Back to Top](#top)

# Software Version {#pkgs}

-   `r version$version.string`

-   FLCore: `r packageVersion('FLCore')`

-   ggplotFL: `r packageVersion('ggplotFL')`

-   FLBRP: `r packageVersion('FLBRP')`

-   plyr: `r packageVersion('plyr')`

-   ggpubr: `r packageVersion('ggpubr')`

-   scales: `r packageVersion('scales')`

-   **Compiled**: `r date()`

-   **Git Hash**:
    `r system("git log --pretty=format:'%h' -n 1", intern=TRUE)`

[Back to Top](#top)

# Funding {#funds}

[Back to Top](#top)

# References {#bib}

[Back to Top](#top)

# 
